Macroscopic Salt Rejection through Electrostatically Gated Monolayer Porous Graphene

### 2018-10-03 paper/paper.tex
Drafted version done

\section{Introduction}
\label{sec:intro}
In the emerging field of nanofluidics, a central objective is to
manipulate transport phenomena at nanometer scale to enable new
technological opportunities for sensing and energy applications. The
reduction of characteristic dimensions in nanofluidics gives rise to
substantially different transport properties compared to their bulk
counterparts \cite{Schoch_2008}. In nanopores, for example, the effect
of surface-mediated transport becomes dominant when the pore size is
comparable to the solute diffusion length, enabling new applications,
including ionic diodes \cite{Karnik_2007}, field-effect transistors
\cite{Nam_2009}, desalination \todo[inline]{cite}, and nanopore-based DNA
sequencing \cite{Heerema_2016,Garaj_2013}, Atomically thin
two-dimensional (2D) materials, such as graphene, represent an ideal
category of membrane materials due to their ultimate permeability
\cite{Cohen_Tanugi_2012}. In electrolyte systems, specifically for the
aqueous media, early research has suggested that the separation of
ions by the pore size differentiating the hydrated radii of
$\sim{}$1-3 nm enables excellent salt rejection \todo[inline]{(cite
  Refs. [1-7] in
  https://www.nature.com/articles/ncomms11408.pdf)}. Nevertheless, the
fabrication of sub-5 nanometer porous 2D membranes over a large area
with atomic precision is technically challenging \cite{Suk_2014}
\todo[inline]{also Refs [8], [9] in the nature comm paper, as well as the
  nature comm paper itself}. Moreover, a small portion of large pores
can significantly diminish salt rejection. To address these issues,
recent research efforts have been focused on control over the surface
charges by chemical functionalization \todo[inline]{cite 7-13}. However, it
remains controversial that if the surface charges can result in a
degree of salt rejection, as the membrane potential is sensitive to
the surroundings and chemical treatment \todo[inline]{onecite}. The difficulty
in turn hinders fundamental understanding of the interactions between
the atomically thin 2D membrane and electrolyte solution. Here, we
demonstrate macroscopic salt rejection through a sheet of large-area
porous monolayer graphene using electrostatic gating.

@@

Figure \ref{fig:1}a presents the experimental setup characterizing
ionic diffusion through a sheet of monolayer porous graphene (PG). Two
reservoirs, namely the high-concentration reservoir (HCR) containing
electrolyte solution with molar concentration $c_0$, and the
low-concentration reservoir (LCR) containing de-ionized (DI) water,
are separated by a PG membrane supported by polycarbonate track-etched
(PCTE) film. Magnetic stirrers are used to minimize the mass transfer
resistance in both reservoirs, and a conductivity probe is placed in
the LCR to monitor the ionic concentration as a function of time. The
membrane is attached to a piece of copper tape connected to a voltage
source applying an electrical bias VG, with the LCR grounded (Figure
\ref{fig:1}a inset). We fabricated the PCTE-supported PG using the
protocol developed by our group \todo[inline]{cite}, as schematically shown in
Figure \ref{fig:1}b. By optimizing the process, a high surface
coverage (> 98\%) of graphene on PCTE was reached (Figure
\ref{fig:1}c), allowing us to reliably characterize the ion transport
behavior (details see Supplementary Information Section S1). The
circular pores with pore diameters of 20$\pm$10 nm (Figure
\ref{fig:1}c inset) over a large area were drilled on monolayer
graphene. The system presented here allows us to systematically
investigate the diffusive flux across a sheet of porous graphene,
$\boldsymbol{J}$, driven by the gradient of electrochemical potential in
the electrolyte medium.

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$Fe(CN)$_{6}$,
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity versus time profile
(e.g. Figure \ref{fig:2}a) remains linear within the measurement
duration ($\sim{}$1 h), suggesting the concentration change in
individual reservoirs is negligible \todo[inline]{really?}. The diffusive
fluxes correspond to different salts were obtained by converting the
conductivity-time profiles with the calibration curves (blue bars in
Figure \ref{fig:2}b and Supplementary Figure S2). On the other hand,
for comparison purposes, based on the assumption that the membrane is
composed of cylindrical pores with uniform diameter and a low
tortuosity $\tau$ of $\sim{}$1.2 \todo[inline]{cite 14}, the molar diffusive
flux through the bare PCTE membrane,
$\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}
where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
and $\tau$ is the tortuosity. By using the salt diffusivity values
provided by the PTCE vendor (Supplementary Table SXX \todo[inline]{ref}), the
calculated diffusive fluxes (red bars in Figure \ref{fig:2}b) show
reasonable agreement with the experimental values.

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
Figure \ref{fig:2}b), remain at the same order of magnitude compared
to those of bare PCTE membrane, suggesting that the mass transfer
resistance of PG is not significant, as the permeability is high. We
observed a more pronounced decrease of diffusive flux in KCl, K$_{2}$SO$_{4}$
and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest of the salts. We
hypothesized that the strong cation-$\pi$ interactions between K$^{+}$ cations
and graphene \todo[inline]{15} slow down the migration of cations along the
surface-mediated transport pathway, which has been proven as a strong
contributor at low concentration \todo[inline]{cite}.

@@

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which had been used
in controlling the membrane potential in mesoporous carbon membranes
\todo[inline]{8}, is adopted here. Figure \ref{fig:2}a presents a
representative data of the measured conductivity with respect to
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile corresponding to the diffusive flux through
the PG-PCTE membrane, giving the average slope $s_{1}$. In the second
interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane after
turning off the conductivity probe, followed by the third interval, in
which the conductivity probe is turned on again to give the
corresponding slope, $s_{3}$. The slope corresponding to the second
interval, $s_{2}$, as the conductivity probe is off, is determined by
linearly interpolating the conductivities from the endpoint of
interval 1 to the starting point of interval 3. Accordingly, we define
the salt rejection factor, $\xi$, which is effectively equivalent to
the relative degree of diffusive flux decrease as follows:
\begin{equation}
  \label{eq:rejection}
  \xi = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{2}$, namely
$(s_{1} + s_{2})/2$ \todo[inline]{Should this be $(s_{1}+s_{3})/2$?},
and $\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive
flux across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. Note that a positive $\xi$ between 0 and 1
represents a decrease of the diffusive flux. The factor $\xi$ enables a
reliable and stable measurement of salt rejection, as the salt species
and initial conditions may induce a degree of measurement uncertainty
between different samples. A control experiment was performed to
ensure the copper tape was not in direct contact with the ionic
solution (Supplementary Section 3).

Using 0.1 mM KCl solution in HCR, we measured $\xi$ as a function of
$V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
electrochemical reactions (Figure \ref{fig:2}c). We observe an
asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
positive carriers (holes) are induced in graphene. We notice that an
increase $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$ with
$V_{\mathrm{G}}$, showing an inverse trend compared to those observed
in ionic field effect transistors (IFETs) \todo{cite}, in which the
diffusive flux increases with the gate voltage \todo{cite 3, 23}. A
further increase of the KCl concentration $c_{0}$ influences the
attainable degree of salt rejection. $\xi$ values measured at
$V_{\mathrm{G}}$=1.25 V, $\xi_{\mathrm{max}}$, as a function of
$c_{0}$ from 10$^{-4}$ to 10$^{-2}$ M KCl (see Supplementary Section
S4) exhibit a power law dependency (Figure \ref{fig:2}d). The
$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
law function following
$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Const}$. As the Debye
screening length in solution, $\lambda_{\mathrm{D}}$, is inversely
proportional to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced
salt rejection originates from the modulation of the electrical double
layer (EDL), as will be discussed later.

@@

approximation holds. Accordingly, the steady-state Nernst-Planck equation
describing the ionic transport in an electrolyte solution is given by \todo{cite}:

@@

of ideal solution, it follows \todo{cite}:

@@

Stern layer \todo{for graphene?}, and $\varepsilon_{0}$ is the vacuum
permittivity. When applying $V_{\mathrm{G}}$ to graphene adjacent to
the electrolyte solution, charges (electrons or holes) are induced in
graphene; the electroneutrality of the entire system suggests:

@@

graphene quantum capacitance effect \todo{cite-24} (Figure

@@

using the finite-element method, in which the graphene surface

@@

during synthesis and patterning \todo{25}, effectively increasing the
graphene quantum capacitance for $V_{\mathrm{G}}<0$ (Supplementary
Figure SXX \todo{ref}). With the nonideality in mind, hereafter, we
compare the calculations and experiments in the regime of
$V_{\mathrm{G}}>0$. For example, Figure \ref{fig:3}c presents the

@@

$\psi_{\mathrm{G}}$ tp $\sim{}$0.3 V at $V_{\mathrm{G}}=1.25$ V,

@@

$\sim{}$0.08 C$\cdot$m$^{-2}$. Note that as we mentioned earlier, an

@@

as a fitting parameter as in most of the 2D nanopore studies,
\todo{cite 18}.

\subsection{Salt rejection mechanism}
\label{sec:mechanism}
The numerical procedure described above allows us to resolve the
concentration and electric potential profiles near to a graphene
nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
by both $\psi$ and $c$ fields (see Eq. \ref{eq:pnp} and \ref{eq:mu}),
we focus on the electrochemical potential $\mu_{i}$, which represents
the combined driving force, to reveal its dependence on the applied
$V_{\mathrm{G}}$. Following the same system considered in Figure
\ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
and the relative electrochemical potentials,
$\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
$V_{\mathrm{G}}=0.75$ V are shown in Figure \ref{fig:4}a and
\ref{fig:4}b, respectively. \todo[inline]{say somthing} The reference point of the electrochemical
potentials is set at the bulk phase in the HCR. As expected, the
electric potential reaches the maximum at the graphene surface (with
$\psi_{\mathrm{G}}$ of $\sim{}$100 mV) and decays towards the bulk
solution phase, forming an EDL surrounding the graphene surface. Since
the Debye screening length $\lambda_{\mathrm{D}}$ is comparable to the
pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
center remains at $\sim{}$25 mV, comparable to the thermal energy at
room temperature ($k_{\mathrm{B}}T=$26 meV). Consequently, it is
evident that the potential barrier is sufficient to modulate the
diffusive flux.

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (Figure \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes small. The
observation confirms the distinct ionic transport pathways upon
applying a positive $V_{\mathrm{G}}$: pore center for cations and pore
edge for anions. Figure \ref{fig:4}c presents the calculated
z-component of the cation and anion fluxes through the pore at the
graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of the
normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
because the LCR is placed at z < 0 in the simulations. At
$V_{\mathrm{G}}=$0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (Figure \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see Figure \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \todo{cite 18}.

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \todo{3,26,27}. To this end, we further increased the
graphene surface potential $\psi_{\mathrm{G}}$ considering the same
system (Supplementary Section 6 \todo{confirm}). Intriguingly, by
increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
starts to increase, reversing the trend observed at the low
$\psi_{\mathrm{G}}$ regime, because of an increase of cation diffusion
\todo{note!}. This level of $\psi_{\mathrm{G}}$ cannot be reached
experimentally in graphene membrane, as this requires a
$V_{\mathrm{G}}$ larger than 2.0 V \todo{confirm}, which triggers the
electrochemical reactions. On the other hand, in an IFET, the electric
potential on the pore wall is considerably higher, equivalent to
$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
an infinitely-large quantum capacitance). We therefore conclude that
the quantum capacitance-induced nonlinear damping in the surface
potential results in the observed salt rejection.  Following the above
discussions, we further investigate the physical limits for the biased
graphene nanopores. Specifically, the salt rejection characteristics
are controlled by: (i) the overlap of EDL inside the nanopore,
essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
and $R_{\mathrm{G}}$, and (ii) the graphene surface potential
$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
Eq. \ref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$ (Figure \ref{fig:5}a). Clearly, when the bulk
concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
revealed in Figure \ref{fig:5}b, the calculated salt rejection factor
$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$, in line with the experimentally observed
$\xi - c_{0}$ dependence. We also find the overall trends for
$\psi_{\mathrm{G}}$ and $\xi$ with respect to
$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$=1.25 V and
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$=1.0, a high value of $\xi$ of
$>$0.85 can be achieved.

>>>>

\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
manipulate transport phenomena at nanometer scale to enable new
technological opportunities for sensing and energy applications. The
reduction of characteristic dimensions in nanofluidics gives rise to
substantially different transport properties compared to their bulk
counterparts \cite{Schoch_2008}. In nanopores, for example, the effect
of surface-mediated transport becomes dominant when the pore size is
comparable to the solute diffusion length, enabling new applications,
including ionic diodes \cite{Karnik_2007}, field-effect transistors
\cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
atomically thin two-dimensional (2D) materials, such as graphene,
embody an ideal membrane materials due to their ultimate permeability
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using nanoporous graphene as the
desalination membrane enables excellent salt rejection by preventing
the permeation of the hydrated ions the (1 nm - 3 nm) with
simultaneous high water permeation
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2015,Surwade_2015}. Nevertheless,
the fabrication of sub-5 nanometer porous 2D membranes over a large
area with atomic precision is technically challenging
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of large pores can significantly diminish salt rejection.
Accordingly, recent research efforts have explored the effect of
surface charges on the selectivity of ion transport, as a consequence
of coulombic repulsion of the solvated ion and the charged functional
groups on graphene \cite{Rollings_2016,Surwade_2014}. However, it
remains controversial that if the surface charges can result in a
degree of salt rejection, as the membrane potential is sensitive to
the surroundings and chemical treatment \cite{Li_2008}. The
difficulty in turn hinders fundamental understanding of the
interactions between the atomically thin 2D membrane and electrolyte
solution. Here, we demonstrate macroscopic salt rejection through a
sheet of large-area porous graphene using electrostatic gating,
thereby deepening the understanding of ion-graphene interaction and
its implications on nanoporous graphene-based desalination
applications.

@@

Figure \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of monolayer porous graphene (PG). Two
reservoirs, namely the high-concentration reservoir (HCR) containing
electrolyte solution with molar concentration $c_0$, and the
low-concentration reservoir (LCR) containing de-ionized (DI) water,
are separated by a PG membrane supported by polycarbonate track-etched
(PCTE) film. Magnetic stirrers are used to minimize the effects of
external concentration polarization, and a conductivity probe is
placed in the LCR to monitor the ionic concentration as a function of
time. The membrane is attached to a piece of copper tape connected to
a voltage source applying an electrical bias $V_{\mathrm{G}}$, with
the LCR grounded (Figure \ref{fig:1}a inset). We fabricated the
PCTE-supported PG using the protocol developed by our group
\cite{Choi_2018}, as schematically shown in Figure \ref{fig:1}b. The
normally distributed, circular pores with pore diameters of 20$\pm$10
nm (Figure \ref{fig:1}c inset) over a large area were drilled on
graphene.  By optimizing the subsequent transfer process, a high
surface coverage (> 98\%) of graphene on PCTE was reached (Figure
\ref{fig:1}c), allowing to reliably characterize the ion transport
behavior (details see Supplementary Information Section S1).  The
system presented here allows us to systematically investigate the
diffusive flux across a sheet of porous graphene, $\boldsymbol{J}$,
driven by the gradient of electrochemical potential in the electrolyte
medium.

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO4$_{4}$, CaCl$_{2}$ and K$_{3}$Fe(CN)$_{6}$,
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity versus time profile
(e.g. Figure \ref{fig:2}a) remains linear within the measurement
duration (1 h), suggesting the concentration change in individual
reservoirs is negligible \todo[inline]{really?}. The diffusive fluxes
correspond to different salts were obtained by converting the
conductivity-time profiles with the calibration curves (blue bars in
Figure \ref{fig:2}b and Supplementary Figure S2). For comparison
purposes, based on the assumption that the membrane consists
cylindrical pores with uniform diameter and a low tortuosity $\tau$ of
$\sim{}$1.2 \cite{O_Hern_2012}, the molar diffusive flux through
the bare PCTE membrane, $\boldsymbol{J}_{\mathrm{PCTE}}$, follows:
  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}
where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity, and $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$, $\delta$ is the thickness of the PCTE membrane,
and $\tau$ is the tortuosity. By using the salt diffusivity values
provided by the PTCE vendor (Supplementary Table S1), the
calculated diffusive fluxes (red bars in Figure \ref{fig:2}b) show
reasonable agreement with the experimental values.

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
Figure \ref{fig:2}b), remain at the same order of magnitude compared
to those of bare PCTE membrane, suggesting that the mass transfer
resistance of PG is not significant, as the permeability is high. We
observed a more pronounced decrease of diffusive flux in KCl,
K$_{2}$SO$_{4}$ and K$_{3}$Fe(CN)$_{6}$ systems but not for the rest
of the salts. We hypothesized that the strong cation-$\pi$ interactions
between K$^{+}$ cations and graphene slow down the migration of cations
along the surface-mediated transport pathway \cite{Sun_2014}.

@@

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which had been used
in controlling the membrane potential in mesoporous carbon membranes
\cite{Surwade_2014}, is adopted here. Figure \ref{fig:2}a presents the
representative data of the measured conductivity with respect to
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile corresponding to the diffusive flux through
the PG-PCTE membrane, giving the average slope $s_{1}$. In the second
interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane after
turning off the conductivity probe, followed by the third interval, in
which the conductivity probe is turned on again to give the
corresponding slope, $s_{3}$. The slope corresponding to the second
interval, $s_{2}$, as the conductivity probe is off, is determined by
linearly interpolating the conductivities from the endpoint of
interval 1 to the starting point of interval 3. Accordingly, we define
the salt rejection factor, $\xi$, which is effectively equivalent to
the relative degree of diffusive flux decrease as follows:
\begin{equation}
  \label{eq:rejection}
  \xi = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
$(s_{1} + s_{3})/2$, and
$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. Note that a positive $\xi$ between 0 and 1
represents a decrease of the diffusive flux. The factor $\xi$ enables
a reliable and stable measurement of salt rejection, as the salt
species and initial conditions may induce a degree of measurement
uncertainty between different samples. A control experiment was
performed to ensure the copper tape was not in direct contact with the
ionic solution (Supplementary Section 3).

Using 0.1 mM KCl solution in HCR, we measured $\xi$ as a function of
$V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
electrochemical reactions (Figure \ref{fig:2}c). We observe an
asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
positive carriers (holes) are induced in graphene. We notice that an
increase $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$ with
$V_{\mathrm{G}}$, showing an inverse trend compared to those observed
in ionic field effect transistors (IFETs), in which the diffusive flux
increases with the gate voltage \cite{Nam_2009,Cheng_2018}. A further
increase of the KCl concentration $c_{0}$ influences the attainable
degree of salt rejection. $\xi$ values measured at
$V_{\mathrm{G}}$=1.25 V, $\xi_{\mathrm{max}}$, as a function of
$c_{0}$ from 10$^{-4}$ to 10$^{-2}$ M KCl (see Supplementary Section
S4) exhibit a power law dependency (Figure \ref{fig:2}d). The
$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
law function following
$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{Constant}$. As the Debye
screening length in solution, $\lambda_{\mathrm{D}}$, is inversely
proportional to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced
salt rejection originates from the modulation of the electrical double
layer (EDL), as will be discussed later.

@@

approximation holds. Accordingly, the steady-state Nernst-Planck
equation describing the ionic transport in an electrolyte solution is
given by \cite{MacGillivray_1968}:

@@

of ideal solution, it follows \cite{Kilic_2007}:

@@

Stern layer\cite{Tian_2017}, and
$\varepsilon_{0}$ is the vacuum permittivity. When applying
$V_{\mathrm{G}}$ to graphene adjacent to the electrolyte solution,
charges (electrons or holes) are induced in graphene; the
electroneutrality of the entire system suggests:

@@

graphene quantum capacitance effect\cite{Xia_2009} (Figure

@@

using the finite-element method (FEM), in which the graphene surface

@@

during synthesis and patterning \cite{Dean_2010}, effectively
increasing the graphene quantum capacitance for $V_{\mathrm{G}}<0$
(Supplementary Figure SXX \todo{ref}). With the nonideality in mind,
hereafter, we compare the calculations and experiments in the regime
of $V_{\mathrm{G}}>0$. For example, Figure \ref{fig:3}c presents the

@@

$\psi_{\mathrm{G}}$ tp $\sim$0.3 V at $V_{\mathrm{G}}$=1.25 V,

@@

$\sim$0.08 C$\cdot$m$^{-2}$. Note that as we mentioned earlier, an

@@

as a fitting parameter as in most of the 2D nanopore studies
\cite{Rollings_2016}.

\subsection{Salt rejection mechanism}
\label{sec:mechanism}
The numerical procedure described above allows us to resolve the
concentration and electric potential profiles near to a graphene
nanopore for a given $V_{\mathrm{G}}$. Since the ionic flux is driven
by both $\psi$ and $c$ fields (see Eq. \ref{eq:pnp} and \ref{eq:mu}),
we focus on the electrochemical potential $\mu_{i}$, which represents
the combined driving force, to reveal its dependence on the applied
$V_{\mathrm{G}}$. Following the same system considered in Figure
\ref{fig:3}b, the calculated axisymmetric electric potential $\psi$
and the relative electrochemical potentials,
$\Delta \mu_{\mathrm{K^{+}}}$ and $\Delta \mu_{\mathrm{Cl^{-}}}$, for
$V_{\mathrm{G}}$=0.75 V are shown in Figure \ref{fig:4}a and
\ref{fig:4}b, respectively. The reference point of the electrochemical
potentials is set at the bulk phase in the HCR. As expected, the
electric potential reaches the maximum at the graphene surface (with
$\psi_{\mathrm{G}}$ of $\sim$100 mV) and decays towards the bulk
solution phase, forming an EDL surrounding the graphene surface. Since
the Debye screening length $\lambda_{\mathrm{D}}$ is comparable to the
pore radius $R_{\mathrm{G}}$, the electric potential at the nanopore
center remains at $\sim$25 mV, comparable to the thermal energy at
room temperature ($k_{\mathrm{B}}T=$26 meV). Consequently, it is
evident that the potential barrier is sufficient to modulate the
diffusive flux.

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (Figure \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes
small. (also see Supplementary Figures SXX \todo{note}). We also
observe that $\Delta \mu_{+}$ is dominated by the concentration, while
$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
between the diffusion and drift potentials (see Supplementary Figure
SXX \todo{note}). The observations confirm the distinct ionic
transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
center for cations and pore edge for anions. Figure \ref{fig:4}c
presents the calculated z-component of the cation and anion fluxes
through the pore at the graphene plane (z = 0), $\boldsymbol{J}_{z}$
,as a function of the normalized radius, $r/R_{\mathrm{G}}$ , where
$r$ is the radial coordinate and $R_{\mathrm{G}}$ is the pore radius,
at different $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$
is negative because the LCR is placed at z < 0 in the simulations. At
$V_{\mathrm{G}}=$0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (Figure \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see Figure \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \cite{Rollings_2016}.

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (Supplementary Section 6
\todo{confirm}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
larger than 400 mV, the ionic flux starts to increase, reversing the
trend observed at the low $\psi_{\mathrm{G}}$ regime, because of an
increase of cation diffusion \todo{note!}. This level of
$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V
\todo{confirm}, which triggers the electrochemical reactions. On the
other hand, in an IFET, the electric potential on the pore wall is
considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
metallic nature of gate electrode (having an infinitely-large quantum
capacitance). We therefore conclude that the quantum
capacitance-induced nonlinear damping in the surface potential results
in the observed salt rejection.  Following the above discussions, we
further investigate the physical limits for the biased graphene
nanopores. Specifically, the salt rejection characteristics are
controlled by: (i) the overlap of EDL inside the nanopore, essentially
controlled by two length scales of $\lambda_{\mathrm{D}}$ and
$R_{\mathrm{G}}$, and (ii) the graphene surface potential
$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
Eq. \ref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$ (Figure \ref{fig:5}a). Clearly, when the bulk
concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
revealed in Figure \ref{fig:5}b, the calculated salt rejection factor
$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$, in line with the experimentally observed
$\xi - c_{0}$ dependence. We also find the overall trends for
$\psi_{\mathrm{G}}$ and $\xi$ with respect to
$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$=1.25 V and
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$=1.0, a high value of $\xi$ of
$>$0.85 can be achieved.
